Numerical trajectory patterns of floating macroalgae

### 2021-01-20 thesis_chapter_3.Rmd
added in velocity column data wrangling

---
title: 'Numerical trajectory patterns of floating macroalgae'
author: "Ross Coppin"
output:
  word_document:
    reference_docx: markdown/frontiers_template.docx
  pdf_document:
    fig_caption: yes
  html_document:
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

Min_Kfloat_H100_W00$type <- "Min_Kfloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H095_W05$type <- "Min_Kfloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H090_W10$type <- "Min_Kfloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H085_W15$type <- "Min_Kfloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_Kfloat_H100_W00$type <- "Mean_Kfloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H095_W05$type <- "Mean_KFloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H090_W10$type <- "Mean_KFloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H085_W15$type <- "Mean_KFloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H100_W00$type <- "Max_KFloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H095_W05$type <- "Max_KFloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H090_W10$type <- "Max_KFloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H085_W15$type <- "Max_KFloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label

>>>>

---
title: 'Numerical trajectory patterns of floating macroalgae'
author:
- R Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  word_document:
    reference_docx: markdown/frontiers_template.docx
  pdf_document:
    fig_caption: yes
  html_document:
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

Min_Kfloat_H100_W00$type <- "Min_Kfloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00$velocity <- with(Min_Kfloat_H100_W00, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H095_W05$type <- "Min_Kfloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05$velocity <- with(Min_Kfloat_H095_W05, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H090_W10$type <- "Min_Kfloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10$velocity <- with(Min_Kfloat_H090_W10, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H085_W15$type <- "Min_Kfloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15$velocity <- with(Min_Kfloat_H085_W15, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_Kfloat_H100_W00$type <- "Mean_Kfloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00$velocity <- with(Mean_Kfloat_H100_W00, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H095_W05$type <- "Mean_KFloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05$velocity <- with(Mean_KFloat_H095_W05, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H090_W10$type <- "Mean_KFloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10$velocity <- with(Mean_KFloat_H090_W10, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H085_W15$type <- "Mean_KFloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15$velocity <- with(Mean_KFloat_H085_W15, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H100_W00$type <- "Max_KFloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00$velocity <- with(Max_Kfloat_H100_W00, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H095_W05$type <- "Max_KFloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05$velocity <- with(Max_Kfloat_H095_W05, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H090_W10$type <- "Max_KFloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10$velocity <- with(Max_Kfloat_H090_W10, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H085_W15$type <- "Max_KFloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15$velocity <- with(Max_Kfloat_H085_W15, sqrt(kelpvelU^2 + kelpvelV^2))
